---
title: "Create Composites"
author: "Juan Ospina"
date: "3/5/2019"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    number_sections: TRUE
---

```{r global options, echo=FALSE}
source("../R/markdown_global_options.R")
```

```{r}
source("../R/packages.R")
```

```{r}
source("../R/custom_functions.R")
```

```{r}
source("../analyzing/list_variables.R")
```

```{r}
ltb <-
  read_rds("../../LTB Data/LTB Intervention Data/Fall '16-Spring '17 & Fall '17-Spring '18 Intervention Data (Filtered).rds")
```

# Pre-Measures

## Grit

```{r}
# Get variables names
get_names(ltb, "s0.grit")

# Subscales of composite
vars <-
  c(
    "s0.grit_finish",
    "s0.grit_project",
    "s0.grit_try",
    "s0.grit_goals",
    "s0.grit_quitting" 
  )

# Scale reliability
alphatize_2(ltb, quos(vars))

# Fitting 1-5 Factor Model
# extract a single factor with no rotation (since only one factor) 
# with maximum likelihood estimation
singfac <- fa(select(ltb, !!!quos(vars)), 
              nfactors = 1, rotate = "none", SMC = TRUE, 
              fm = "ml", alpha = .05, n.iter = 1000)
singfac

# Second way to conduct a factor analysis
factor_analysis(ltb, quos(vars), 1)

# Create composite
ltb$s0.grit_c5 <- 
  composite(select(ltb, !!!quos(vars)), 
            Zitems = FALSE, rel = TRUE, nomiss = .33)
```

## Implicit Theories of Personality

Note: Higher values mean more fixed view of personalities.

```{r}
# Get variables names
get_names(ltb, "s0.personality")

# Subscales of composite
vars <-
  c(
    "s0.personality_certain",
    "s0.personality_olddog",
    "s0.personality_change"
  )

# Scale reliability
alphatize_2(ltb, quos(vars))

# Fitting 1-5 Factor Model
# extract a single factor with no rotation (since only one factor) 
# with maximum likelihood estimation
singfac <- fa(select(ltb, !!!quos(vars)), 
              nfactors = 1, rotate = "none", SMC = TRUE, 
              fm = "ml", alpha = .05, n.iter = 1000)
singfac

# Second way to conduct a factor analysis
factor_analysis(ltb, quos(vars), 1)

# Create composite
ltb$s0.personality_c5 <- 
  composite(select(ltb, !!!quos(vars)), 
            Zitems = FALSE, rel = TRUE, nomiss = .33)
```

## Succeed at School

```{r}
# Get variables names
get_names(ltb, "s0.school")

# Subscales of composite
vars <-
  c(
    "s0.school_imp",
    "s0.school_success"
  )

# Scale reliability
alphatize_2(ltb, quos(vars))

ltb %>% 
  corr_table(quos(vars))


# Create composite
ltb$s0.school_c2 <- 
  composite(select(ltb, !!!quos(vars)), 
            Zitems = FALSE, rel = TRUE, nomiss = .33)
```

## Police Concerns & Expectations Because of J.D.

```{r}
# Get variables names
get_names(ltb, "s0.fight")

# Subscales of composite
vars <-
  c(
    "s0.fight_conc",
    "s0.fight_expect"
  )

# Scale reliability
alphatize_2(ltb, quos(vars))

ltb %>% 
  corr_table(quos(vars))


# Create composite
ltb$s0.police_c2 <- 
  composite(select(ltb, !!!quos(vars)), 
            Zitems = FALSE, rel = TRUE, nomiss = .33)
```

# Post-Intervention Outcomes

## Belonging at School

Note: The cleaned dataset already had the "s1.belong_outsider" item reverse-coded. This is why we don't need to do anything in the code below to account for this.

```{r}
# Get variables names
get_names(ltb, "s1.belong")

# Subscales of composite
vars <-
  c(
    "s1.belong_belong",
    "s1.belong_fit",
    "s1.belong_outsider",
    "s1.belong_comfort"
  )

# Scale reliability
alphatize_2(ltb, quos(vars))

# Fitting 1-5 Factor Model
# extract a single factor with no rotation (since only one factor) 
# with maximum likelihood estimation
singfac <- fa(select(ltb, !!!quos(vars)), 
              nfactors = 1, rotate = "none", SMC = TRUE, 
              fm = "ml", alpha = .05, n.iter = 1000)
singfac

# Second way to conduct a factor analysis
factor_analysis(ltb, quos(vars), 1)

# Create composite
ltb$s1.belong_c4 <- 
  composite(select(ltb, !!!quos(vars)), 
            Zitems = FALSE, rel = TRUE, nomiss = .33)
```

## Class Anxiety

```{r}
# Get variables names
get_names(ltb, "s1.anx")

# Subscales of composite
vars <-
  c(
    "s1.anx_teacher",
    "s1.anx_question"
  )

# Scale reliability
alphatize_2(ltb, quos(vars))

ltb %>% 
  corr_table(quos(vars))


# Create composite
ltb$s0.classanx_c2 <- 
  composite(select(ltb, !!!quos(vars)), 
            Zitems = FALSE, rel = TRUE, nomiss = .33)
```

## Fairness at School

```{r}
# Get variables names
get_names(ltb, "s1.fair")

# Subscales of composite
vars <-
  c(
    "s1.fair_eval",
    "s1.fair_disc"
  )

# Scale reliability
alphatize_2(ltb, quos(vars))

ltb %>% 
  corr_table(quos(vars))


# Create composite
ltb$s1.schoolfair_c2 <- 
  composite(select(ltb, !!!quos(vars)), 
            Zitems = FALSE, rel = TRUE, nomiss = .33)
```

## Feeling of Safety

```{r}
# Get variables names
get_names(ltb, "s1.safe")

# Subscales of composite
vars <-
  c(
    "s1.safe_out",
    "s1.safe_travel",
    "s1.safe_hall",
    "s1.safe_class" 
  )

# Scale reliability
alphatize_2(ltb, quos(vars))

# Fitting 1-5 Factor Model
# extract a single factor with no rotation (since only one factor) 
# with maximum likelihood estimation
# singfac <- fa(select(ltb, !!!quos(vars)), 
#               nfactors = 1, rotate = "none", SMC = TRUE, 
#               fm = "ml", alpha = .05, n.iter = 500)
# singfac

# Second way to conduct a factor analysis
factor_analysis(ltb, quos(vars), 1)

# Create composite
ltb$s1.safety_c4 <- 
  composite(select(ltb, !!!quos(vars)), 
            Zitems = FALSE, rel = TRUE, nomiss = .33)
```

## Belonging at School

```{r}
# Get variables names
get_names(ltb, "s2.belong")

# Subscales of composite
vars <-
  c(
    "s2.belong_belong",
    "s2.belong_fit",
    "s2.belong_outsider",
    "s2.belong_comfort"
  )

# Scale reliability
alphatize_2(ltb, quos(vars))

# Fitting 1-5 Factor Model
# extract a single factor with no rotation (since only one factor) 
# with maximum likelihood estimation
singfac <- fa(select(ltb, !!!quos(vars)), 
              nfactors = 1, rotate = "none", SMC = TRUE, 
              fm = "ml", alpha = .05, n.iter = 1000)
singfac

# Second way to conduct a factor analysis
factor_analysis(ltb, quos(vars), 1)

# Create composite
ltb$s2.belong_c4 <- 
  composite(select(ltb, !!!quos(vars)), 
            Zitems = FALSE, rel = TRUE, nomiss = .33)

ltb %<>%
  mutate(
    s2.belong_diff = s2.belong_c4 - s1.belong_c4
    # s2.belong_c4_z = base::scale(s2.belong_c4),
    # s1.belong_c4_z = base::scale(s1.belong_c4),
    # s2.belong_diff_z = s2.belong_c4_z - s1.belong_c4_z
  )

# vars <-
#   c(
#     "s2.belong_c4",
#     "s1.belong_c4"
#   )

# Create composite
# ltb$s2.belong_c4_z <- 
#   composite(select(ltb, !!!quos(vars)), 
#             Zitems = TRUE, rel = TRUE, nomiss = .33)

# Standardize list of variables
# id <- ltb %>% select(Participant)
# vars_std <- standardize_list_vars(ltb, quos(vars))

# merge data 
# ltb %<>% left_join(vars_std, by = "Participant") 
```

```{r}
# ltb <- ltb %>%
#   mutate(
#     s2.belong_c4_z = scale(s2.belong_c4),
#     s1.belong_c4_z = scale(s1.belong_c4),
#     s2.belong_diff_z = s2.belong_c4_z - s1.belong_c4_z
#   )

# ltb %>%
#   select(
#     s2.belong_diff_z, s2.belong_c4_z, s1.belong_c4_z
#   )
```


# Clean condition

```{r}
get_names(ltb, "cond")

ltb %<>% 
  mutate(
    cond = as.factor(Condition),
    cond = factor(
      cond,
      levels = c(1, 
                 2,
                 3),
      labels = c("control", 
                 "intv",
                 "letter")
    )
  )

ltb %>% 
  count(Condition, cond)
```



```{r export cleaned dataset}
ltb %>% 
  write_csv("../../LTB Data/LTB Intervention Data/Fall '16-Spring '17 & Fall '17-Spring '18 Intervention Data (Filtered & cleaned).csv")

ltb %>% 
  write_rds("../../LTB Data/LTB Intervention Data/Fall '16-Spring '17 & Fall '17-Spring '18 Intervention Data (Filtered & cleaned).rds")
```

