---
title: "Open Response Coding"
author: "Elizabeth Weitz"
date: "March 18, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Notes from Shannon's Spontaneous Self-Affirmation protocol for coding ORs

Dimension scales
  Bimodal 0-4 (2 = Neutral)
  Unimodal 0: None;  1: A little;  2: Some;  3: A lot
  Binary 0 = "No", 1 = "Yes"
  Frequency count of some dimensions (how to choose which ones?)

ICC
  For variables with more than two levels, the ICC was calculated using the consistency statistic. 
  For binary variables, ICC was calculated using the exactstatistic.


Questions
Code Session 2 to start - ask Greg on 3/24 if we should also code Session 1 

## Session 1
  
  Control
    Why are study skills important?
    What kinds of study skills can students develop?
    We think it will be most helpful for future students if they hear directly from you, in your own voice, instead of just seeing words on paper.
    What is a study skill you would like to get better at in school, for instance one you might not use well now?
    
  Intervention
    3: Students’ experience in school got better in two ways: 
      a) One way was that students said it helped to think about what was important to them personally....What's important to you? Below are some ideas from other students. Please circle 1 to 3 things.
        Pick one you circled above. Tell us why this is important to you.
    What challenges do students face when coming back to school in Oakland from the Juvenile Detention system? 
    How can positive relationships with teachers and other adults in school help students have a better experience in school?
    How can students develop better relationships with teachers and other adults in school?
    Who is an adult in school you would like to get to know better, for instance, someone you do not know well yet?
      1. What would you like your teacher to know about who you are as a person and what is important to you? Write 1-2 things.
      2. What would you like your teacher to know about your goals in school? Write 1-2 things. 
      3. What would you like your teacher to know about what is difficult for you in school that you would like to improve, so they can help? Write 1-2 things.
      
# Session 2

## Please describe how your experience in school has or has not changed since our last session.
attendance: Going to school/classes more (0,1)
Work: commitment, making an effort to complete HW, study more, take classes previously failed (0,1)
focus: commitment, mentioning mental commitment i.e paying attention, more focus (0,1)
growth: did things change, in what direction? (2: positive; 1: neutral; 0: negative)
construal: are things better, the same, or worse? (2: better; 1: the same; 0: worse)
relationships: did they mention them or not? (0,1)

```{r}
d$s2.school_changed
# write.csv(d[,c(1,116,117)], "S2QualitativeCoding.csv") # participant, school_changed, and school_improve
```

## Please describe what if anything you have done since our last session to improve your experience in school?
Attendance: Going to school/classes more (0,1)
commitment_Work: making an effort to complete HW, study more, take classes previously failed (0,1)
commitment_focus: mentioning mental commitment i.e paying attention, more focus (0,1)
growth: did things change, in what direction? (2: positive; 1: neutral; 0: negative)
general_construal: are things better, the same, or worse? (2: better; 1: the same; 0: worse)
count_relationships: did they mention them or not? (0,1)

```{r}

d$s2.school_improve
```

## 
Make 
